% This file was converted to LaTeX by Writer2LaTeX ver. 1.4
% see http://writer2latex.sourceforge.net for more info
\documentclass{article}
\usepackage[ascii]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amssymb,amsfonts,textcomp}
\usepackage{array}
\usepackage{hhline}
\usepackage[top=1.25in, bottom=1.25in, left=1.25in, right=1.25in]{geometry}
\title{}
\linespread{2}
\begin{document}
Ian MacGregor

Instructor Cesar Torres

Computer Science 24

23 April 2015

\begin{center}
Research Seminar Summary 2
\end{center}

\ \ I attended two seminars: Human-Centered Computer Security (one hour) and Policing the Police: Researching Civilian Oversight Boards (two hours). 

\ \ The second, Policing the Police: Researching Civilian Oversight Boards, was held at the Berkeley School of Law and concerned the complex issue of holding law enforcement officials accountable for their unlawful actions using civilian review boards. The research seminar was conducted by four opposing officials in different fields related to law enforcement, including Jim Chanin, a Civil Rights Attorney, Captain Majit Sappal, a Richmond Police Department Officer, Rashidah Grinage, the director of People United for a Better Life in Oakland (PUEBLO), and Mark Smith, an independent police auditor for BART. They each spoke about their varying experiences with a civilian review board or lack there of. 

\ \ One insight I found interesting, made by Rashidah Grinage, was that we live in a democracy where all power comes from civilians and which begs the question ``Why are police any different?'' Another insight I found interesting, made by Captain Majit Sappal, was that every american is entitled to a jury of their peers, hence why civilians need a civilian jury and police officers need a police jury. One oversight I found was that there were many slippery slope arguments in regards to the US becoming a Police State and the Police becoming overridden by civilian oversight. I really didn't understand civilian oversight boards, and now I do! They are boards of civilians which advise or confirm decisions in regards to discipline of police. 
\end{document}
